### 2014-05-22 patchy-selection-paper.tex
added Lava_flow_mice_app.R Lava_flow_mice_prob_parallel.pdf

As can be seen from the above, a key parameter is the characteristic length $\sigma/\sqrt{s_m}$. 
\citep{Hoekstra:04} studied the frequency of the dark MC1R allele, and coat color phenotypes, at sites on the Pinacate lava flow and at two nearby sites in light-colored rock.
On the lava flow the dark MC1R allele is at 86\% frequency. 
At the Tule light substrate site, which is $\sim$ 12km from the flow, the dark MC1R allele was at $\sim$ 3\% frequency. 
At a greater distance from the lava (XXXkm) the light colored substrate the dark MC1R was absent from a sample at the Christmas pass. 
While at the other light substrate site (O'Neill), which is 10km from the flow on opposite side from Tule, 
the dark MC1R allele has a frequency of $\sim$ 34\%. 
On the basis of these numbers we can gain a sense of a plausible range of characteristic lengths.
Assuming the allele is at 50\% frequency at the edge of the lava flow, 
we can fit the frequency found at each of the light substrate sites that are 
polymorphic for the dark allele under a simple allele frequency cline model \citep{XXX}.
Doing this for the Tule we obtain $\sigma/\sqrt{s_m} \approx 4$km and for the O'Neill site
$\sigma/\sqrt{s_m} \approx 30$km.

The mutational target size $\mu$ for the trait is unclear. 
While the Pinacate dark haplotype differs from the light haplotype at three amino-acid residues,
it is likely that not all of these changes are needed for a population to begin to  
adapt. Also there a number of genes, beyond MC1R, at which adaptative changes affecting 
pigmentation have been identified in closely related species and more
broadly across vertibrates \citep{}.To span a range of plausible
values, we use a low mutation rate 
We use a low mutation rate $\mu= 10^{-8}$, where the adaptive
mtation has to occur at a single base pair.
An intermediate mutation rate $\mu= 10^{-5}$, equivalent to
the mutation being able to arise at any of a thousand bases pairs,
e.g. any of the coding bases of a typical length gene. And a high
mutation rate $\mu = 10^{3}$, corresponding to the adaptive mutation
being able to arise in any of $100$ genes, e.g. anywhere in a large pathway.

>>>>

As can be seen from the above, a key parameter is the characteristic length $\sigma/\sqrt{s_m}$. 
\citep{Hoekstra:04} studied the frequency of the dark MC1R allele, and coat color phenotypes, at sites on the Pinacate lava flow and at two nearby sites in light-colored rock.
On the lava flow the dark MC1R allele is at 86\% frequency. 
At the Tule light substrate site, which is $\sim$ 12km from the flow, the dark MC1R allele was at $\sim$ 3\% frequency. 
At a greater distance from the lava (XXXkm) the light colored substrate the dark MC1R was absent from a sample at the Christmas pass. 
While at the other light substrate site (O'Neill), which is 10km from the flow on opposite side from Tule, 
the dark MC1R allele has a frequency of $\sim$ 34\%. 
On the basis of these numbers we can gain a sense of a plausible range of characteristic lengths.
Assuming the dark allele is at 50\% frequency at the edge of the lava flow, 
we can fit the frequency found at each of the light substrate sites that are 
polymorphic for the dark allele under a simple allele frequency cline model \citep{XXX}.
Doing this for the Tule we obtain $\sigma/\sqrt{s_m} \approx 3$km and for the O'Neill site
$\sigma/\sqrt{s_m} \approx 30$km, giving us a range of cline widths. We also need estimate of $s_m$,
using  $\sigma=1km$ \gc{REF} our cline widths imply $s_m=3^{-1/2}$ and
$30^{-1/2}$ are reasonable values.

The mutational target size $\mu$ for the trait is unclear. 
While the Pinacate dark haplotype differs from the light haplotype at three amino-acid residues,
it is likely that not all of these changes are needed for a population to begin to  
adapt. Also there a number of genes, beyond MC1R, at which adaptative changes affecting 
pigmentation have been identified in closely related species and more
broadly across vertebrates \citep{REF}.To span a range of plausible
values we use a low mutation rate of $\mu= 10^{-8}$, where the adaptive
mtation has to occur at a single base pair; and a high mutation
rate $\mu= 10^{-5}$, equivalent to the mutation being able to arise at any of a thousand base pairs
e.g. any of the coding bases of a typical length gene.  We set $A=100km^2$ reflecting a patch with a width of $\sim 10km$.
